NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Manuscript.Rmd
replaced trainees with student teachers

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor [@Strobel2017].
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

@@

NFC had a direct, medium negative effect on *reduced personal efficacy*, but this relationship was not mediated by any other variable.
Only when the amount of teaching experience was included as a predictor of self-control next to NFC, a very small indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower *reduced personal efficacy*.
The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
The participants in the study by Grass et al. [-@Grass2018] were teacher trainees with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.
However, one could argue that more experience provides the teacher with a bigger repertoire of coping strategies to enable an efficient exertion of self-control, especially for teachers high in NFC who are intrinsically motivated to find and apply such strategies.

>>>>

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and student teachers [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor [@Strobel2017].
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

@@

NFC had a direct, medium negative effect on *reduced personal efficacy*, but this relationship was not mediated by any other variable.
Only when the amount of teaching experience was included as a predictor of self-control next to NFC, a very small indirect effect via self-control reached significance, indicating that teachers with high NFC and more years of teaching experience have higher self-control and, consequently, lower *reduced personal efficacy*.
The higher self-control that comes with more teaching experience is in line with findings of fluctuations in self-control in young adults, reaching a low point between the age of 15 and 19 [@Oliva2019].
The participants in the study by Grass et al. [-@Grass2018] were student teachers with a mean age of 25.5 years, while the majority of the current sample was between 40 and 59 years old.
Therefore, it is likely that not only the teaching experience itself but also higher age might be associated with higher self-control.
However, one could argue that more experience provides the teacher with a bigger repertoire of coping strategies to enable an efficient exertion of self-control, especially for teachers high in NFC who are intrinsically motivated to find and apply such strategies.
